Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2016-03-18 tese1/08_related_work_rtc.tex
[ADD] together JS more info
[RFT] latex tables\n[ADD]streaming ok

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/webrtc_stack.png}
	\caption{WebRTC protocol Stack}
\end{figure}

@@

\ac{DTLS} is similar to \ac{TLS}, but is used on top of \ac{UDP}.
The main difference is the inclusion of a sequence number per packet that is used for packet re-ordering on reception and protects from duplicated packets. If a packet sequence number is less than the expected sequence number the packet is discarded. If a packet sequence number is greater than the expected sequence number the packet may be enqueued or discarded. By knowing the sequence of messages that are sent and received in \ac{DTLS}, timers are used for packet retransmission avoiding acknowledgment messages.
%RP TLS?

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{figures/basic_protocols.png}
	\caption{Overview of transport protocols}
\end{figure}

>>>>

\newcolumntype{Y}{>{\centering\arraybackslash}X}
%\renewcommand{\arraystretch}{2}

\begin{table}[]
\centering
\label{my-label}
    \begin{tabularx}{\textwidth}{*8{Y}@{}m{0pt}@{}} 
    	\cline{5-8}
		&&&\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{~~~~~~MediaStream~~~~~~} & \multicolumn{2}{c|}{~~~~~~DataChannel~~~~~~} 										&\\[12pt]
		\hline 
		\multicolumn{1}{|c|}{XHR} & \multicolumn{1}{c|}{SSE} & \multicolumn{2}{c|}{WebSocket} & \multicolumn{2}{c|}{SRTP} & \multicolumn{2}{c|}{SCTP} 				&\\[12pt]
		\cline{1-3}\cline{6-8} 
		\multicolumn{3}{|c|}{HTTP 1.X/2.0} & \multicolumn{1}{c|}{~~~~~~~~~~~~~~~~~~} & \multicolumn{1}{c}{~~~~~~~~~~~~~~~~} & \multicolumn{3}{|c|}{Session (DTLS)} 	&\\[12pt]
		\hline
		\multicolumn{4}{|c|}{Session (TLS) - optional} & \multicolumn{4}{c|}{ICE, STUN, TURN} 																		&\\[12pt]
		\hline
		\multicolumn{4}{|c|}{Transport (TCP)} & \multicolumn{4}{c|}{Transport (UDP)} 																				&\\[12pt]
		\hline
		\multicolumn{8}{|c|}{Network (IP)}  																														&\\[12pt]
		\hline
	\end{tabularx}
	\caption{WebRTC protocol Stack}

\end{table}

@@

\ac{DTLS} is similar to \ac{TLS}, but is used on top of \ac{UDP}.
The main difference is the inclusion of a sequence number per packet that is used for packet re-ordering on reception and protects from duplicated packets. If a packet sequence number is less than the expected sequence number the packet is discarded. If a packet sequence number is greater than the expected sequence number the packet may be enqueued or discarded. By knowing the sequence of messages that are sent and received in \ac{DTLS}, timers are used for packet retransmission avoiding acknowledgment messages.
%RP TLS?
%\def\tabularxcolumn#1{m{#1}}
\begin{table}[]
\centering
    \begin{tabularx}{\textwidth}{X|Y|Y|Y|@{}m{0pt}@{}}
\cline{2-4}
                                                     & \textbf{TCP}  & \textbf{UDP}     & \textbf{SCTP}    &\\[12pt]\hline
\multicolumn{1}{|c|}{\textbf{Reliability}}           & reliable      & unreliable       & configurable     &\\[12pt]\hline
\multicolumn{1}{|c|}{\textbf{Delivery}}              & ordered       & unordered        & configurable     &\\[12pt]\hline
\multicolumn{1}{|c|}{\textbf{Transmission}}          & byte-oriented & message-oriented & message-oriented &\\[12pt]\hline
\multicolumn{1}{|c|}{\textbf{Flow control}}          & yes           & no               & yes              &\\[12pt]\hline
\multicolumn{1}{|c|}{\textbf{Congestion control}} 	 & yes           & no               & yes              &\\[12pt]\hline
\end{tabularx}
	\caption{Overview of transport protocols}
\end{table}

### 2016-03-18 tese1/XX_implementation_signaling.tex
[RFT] latex tables\n[ADD]streaming ok

Our signaling protocol consists in send and receiving JSON formated messages over WebSockets by both the server and client.

@@

When a user enters in a group conference, after the page is completely loaded it is created a WebSocket that mantains a connection with our web servers. 
Before creating the web socket, we must identify the user and check if he has permissions to participate in the conference. This is done by retrieving the session id from the cookie provided by the user through the \ac{HTTP} headers. It's important to save de user identification before the socket is created because after the the handshake performed by the \emph{WebSocket} protocol\cite{rfc6455} the \ac{HTTP} context is lost.

@@

@@

The media session is established, the server starts to record any received stream and the client created an \ac{URL} correspondent to the stream location.

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{\textwidth}
    	\includegraphics[width=\textwidth]{figures/signaling}
    \end{subfigure}
    \caption{Signaling sequence diagram}
\end{figure}

>>>>

The signaling protocol could be implemented using \ac{HTTP} messages but they would transport extra information such as \ac{HTTP} headers and would follow a request response signaling mechnism which would not be the best option, as multiple ice candidates can arrive at any time. For that reason bi-directional communications were prefered.

Our signaling protocol consists in send and receiving JSON formated messages over WebSockets by both the server and the client.

@@

When a user enters in a group conference, after the page is completely loaded it is created a WebSocket that mantains a connection with our web servers. 
Before creating the web socket, we must identify the user and check if he has permissions to participate in the conference. The user identification is done by retrieving the session id from the cookie provided by the user through the \ac{HTTP} headers then we retrieve all the information need from database in order to check if the user has permissions to join the conference room. It's important to save de user identification before the socket is created because after the the handshake performed by the \emph{WebSocket} protocol\cite{rfc6455} the \ac{HTTP} context is lost.

@@

The \emph{local session description} contains the session identifier, codecs, containers, transport protocols and ports used per media type. The \emph{local session description} is useful to conclude if the client is receiving only, which means that \ac{KMS} doesn't need to mix, record and analyse streams coming from the user \ac{WebRTC} endpoint.

@@

An \ac{ICE} candidate contains an \ac{IP}, port, used transport protocol and an attribute named \emph{sdpMLineIndex} that is used for mapping to the \emph{remote session description} media type.

Both intervenients test the conectivity of each \ac{ICE} candidate. When a connection is established the user and server start to interchange stream data but other \ac{ICE} candidates may arrive with better connections, when that happens the connection changes seamlessly.

With the media session established, the server starts to record any received stream and the client creates an \ac{URL} correspondent to the stream location.

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{\linewidth}
    	\includegraphics[width=\textwidth]{figures/signaling}
    \end{subfigure}
    \caption{Signaling sequence diagram}
\end{figure}
